Imm algorithm implementation for tracking

### 2020-01-29 Latex/exp.tex
tex update

\begin{multicols}{2}
    \section*{Backgound}
    \justify
        Tracking a object with a changing dynamic require propers algorithms and filters. Retriving physical data with
        observations it's not enough, models achiving the best-fit to our data is needed in order to make a prediction and estimate 
        with reduced uncertainty. Here comes to play a major role the IMM algorithm (Interacting Multiple Models): The data
        from sensor are combined with different dynamical models through the algorithm... 
        \subsection*{Simulation Model}
            The target can move with random movement described by a Markov chain and accordingly two different models of movement
            The tracking are performed with grid of sensors. In order to perform a proper simulation the sensor has assumed to have a limited
            range for the tracking and we cannot retrive any information if target is out. It also took in consideration the power consumption 
            for a possible physical system: to model a more enegy efficient system the sensor can switch to 3 different working condition: On,Off,Idle.
            To achive this goal the sensor is working as a state machine as showned in the figure below:

            Sensors can communicate with the sensors in their neighboorhoods and exchange signal named CanSense and CantSense that regulate the transition
            between differents state.

@@

    \section*{Simulation model implementation}
    Introduction
    \subsection*{Filter}
    \subsection*{Sensor}
    The sensor grid are is composed by a set of sensor that can communicate with each others creating a fully connected graphic
    The single sensor works as a state machine, and change its state accordingly with the signal exchanged with the neighboors.
    \begin{figure}[htp]
        \centering
        \includegraphics[width=2cm, height=2cm]{UntitledDiagram.png}
        \caption{An image of a galaxy}
        \label{fig:galaxy}
    \end{figure}
    \subsection*{Random walk and Unycicle model}
    The target in this simulation can move accordingly to two model: random walk and Unycicle. The genaral expression of the two process it
    \begin{equation}
    X^{+}=\begin{bmatrix} A \\ \end{bmatrix}X(k)+\begin{bmatrix} B \\ \end{bmatrix}u(k) + \begin{bmatrix} G \\ \end{bmatrix}w(k)
    \end{equation}
    State,state and noise matrix associate to the random walk has showned below:
    $$
    X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}
    $$

    $$
    A=\begin{bmatrix}
    1&0&\delta&0\\
    0&1&0&\delta\\
    0&0&1&0\\
    0&0&0&1\\
    \end{bmatrix}
    $$

    $$
    G=\begin{bmatrix}
    \delta^2/2&0\\
    0&delta^2/2\\
    \delta&0\\
    0&\delta\\
    \end{bmatrix}
    $$

    $$
    B= \begin{bmatrix}
        \delta^2/2&0\\
        0&delta^2/2\\
        \delta&0\\
        0&\delta\\
    \end{bmatrix}
    $$
   The unycicle model state representation employed has showned below

>>>>

\begin{multicols}{2}
    \section*{Backgound}
    \justify
        Tracking a object with a changing dynamic require propers algorithms and filters. Retriving physical data with
        observations it's not enough, models achiving the best-fit to our data is needed in order to make a prediction and estimate 
        with reduced uncertainty. Here comes to play a major role the IMM algorithm (Interacting Multiple Models): The data
        from sensor are combined with different dynamical models through the algorithm... 
        \subsection*{Simulation Model}
            The target can move with random movement described by a Markov chain and accordingly two different models of movement
            The tracking are performed with grid of sensors. In order to perform a proper simulation the sensor has assumed to have a limited
            range for the tracking and we cannot retrive any information if target is out. It also took in consideration the power consumption 
            for a possible physical system: to model a more enegy efficient system the sensor can switch to 3 different working condition: On,Off,Idle.
            To achive this goal the sensor is working as a state machine as showned in the figure below: \begin{figure}[htp]
                \centering
                \includegraphics[scale=0.1]{UntitledDiagram.png}
                \caption{An image of a galaxy}
                \label{fig:galaxy}
                \end{figure}
            Sensors can communicate with the sensors in their neighboorhoods and exchange signal named CanSense and CantSense that regulate the transition
            between differents state. Thus implies that not all the sensors receive all the messagge, but only from their Neighboors. The sensors in On state
            create a fully connected graph. The nodes composing the graph changes dynamically with iterations according with the movements of target. The numbers of
            sensors turned on depends on working range choosed and position of target.

@@

    \section*{Simulation model implementation}
    Introduction
    \subsection*{Filter}
    \subsection*{Sensor}
    The sensor grid are is composed by a set of sensor that can communicate with each others creating a fully connected graphic
    The single sensor works as a state machine, and change its state accordingly with the signal exchanged with the neighboors.
    \begin{figure}[htp]
        \centering
        \includegraphics[scale=0.1]{UntitledDiagram.png}
        \caption{An image of a galaxy}
        \label{fig:galaxy}
    \end{figure}
    \subsection*{Random walk and Unycicle model}
    The target in this simulation can move accordingly to two model: random walk and Unycicle. The genaral expression of the two process it
    \begin{equation}
    X^{+}= \textbf{A}X(k) + \textbf{B}u(k) + \textbf{G}w(k)
    \end{equation}
    State,state and noise matrix associate to the random walk has showned below:
    \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
        1&0&\delta&0\\
        0&1&0&\delta\\
        0&0&1&0\\
        0&0&0&1\\
        \end{bmatrix}
        G=\begin{bmatrix}
            \delta^2/2&0\\
            0&\delta^2/2\\
            \delta&0\\
            0&\delta\\
            \end{bmatrix}
        \]
        The \textbf{B} input matrix change accordingly with the acceleration input
    \[
        B=\begin{bmatrix}
            \delta^2/2 & 0\\
            0 & 0  \\
            \delta & 0 \\
            0 & 0 \\
            \end{bmatrix}
            B=\begin{bmatrix}
                0 & 0 \\
             0 & \delta^2/2 \\
            0 & 0 \\
            0 & \delta \\
            \end{bmatrix}
  \]
   The unycicle model state representation employed has showned below
